---
title: "new_run_ds_offset"
output: html_document
---

```{r setup, include=FALSE}
rm(list = ls())
library(lubridate)
library(dplyr)
library(plyr)
library(tidyr)
library(ggpmisc)
library(gridExtra)
library(grid)
library(png)
# devtools::install_github("renkun-ken/formattable")
library(formattable)
path.working <- "/Users/laurapuckett/Documents/Research/Fall 2018/"
setwd(path.working)
path.my.files <- paste(path.working, "/my_files/",sep = "")
NOAA.flux <- readRDS(paste(path.working, "my_files/","NOAA.flux.forecasts", sep = ""))
NOAA.state <- readRDS(paste(path.working, "my_files/","NOAA.state.forecasts", sep = ""))
NOAA.data = inner_join(NOAA.flux, NOAA.state, by = c("forecast.date.hour","ensembles"))
obs.data <- read.csv(paste(path.working, "my_files/", "FCRmet.csv", sep = ""),header = TRUE) %>%
  dplyr::mutate(AirTC_Avg = ifelse(AirTC_Avg > 44, NA, AirTC_Avg),
                SR01Up_Avg = ifelse(SR01Up_Avg < 0, 0, SR01Up_Avg)) # get rid of really high temp values that are sensor malfunction

setwd(path.my.files)
source("match_units.R")
source("agg_and_join.R")
source("spline_NOAA_offset.R")
source("new_spline_NOAA_offset.R")
source("new.plot_spline.R")
source("summary_plottting.R")
source("debias_and_add_error.R")
source("daily_debias_and_add_error.R")
source("solar_geom.R")
```

```{r match and join datasets}
forecast.units.match = match_units(obs.data, NOAA.data)[[2]]
forecast.units.match[,"group.num"] = row(forecast.units.match)[,1]
obs.units.match = match_units(obs.data, NOAA.data)[[1]] %>%
   dplyr::mutate(doy_minutes = doy,
          doy = formattable(ifelse(minute == 0, round(yday + hour/24,4),NA),4))
joined.data.original <- agg_and_join(obs.units.match, forecast.units.match) %>% ### only to be used for states, not fluxes!!! Fluxes are not aggregated by group like they should be
  mutate(yday = yday(timestamp))  %>%
  dplyr::group_by(NOAA.member, yday)  %>%
  # force NA for days without 4 NOAA entries
  dplyr::mutate(n = n(),
                temp.for = ifelse(n == 4, temp.for, NA), 
                RH.for = ifelse(n == 4, RH.for, NA),
                ws.for = ifelse(n == 4, ws.for, NA),
                avg.sw.for = ifelse(n==4, avg.sw.for, NA),
                avg.lw.for = ifelse(n==4, avg.lw.for, NA),
                precip.rate.for = ifelse(n==4, precip.rate.for, NA)) %>%
  ungroup()

ggplot(data = joined.data.original,aes(x = temp.for, y = temp.obs)) +
  geom_point(alpha = 0.8, color = "darkolivegreen4", size = .8) +
  geom_smooth(method = "lm", se = FALSE, color = "black", formula = y~x) +
  stat_poly_eq(formula = y~x, 
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
               parse = TRUE) +
  xlab("NOAA Forecast") +
  ylab("Site Observations") +
  ggtitle("Temperature [C], 6-Hourly Measurements Comparison") + 
  theme(text = element_text(size=15))
```

```{r aggregate to daily}
joined.data.daily <- joined.data.original %>%
  dplyr::group_by(NOAA.member, yday) %>%
  dplyr::summarize(temp.obs = mean(temp.obs, na.rm = FALSE), # getting daily means from minute or 6-hourly
                   RH.obs = mean(RH.obs, na.rm = FALSE),
                   ws.obs = mean(ws.obs, na.rm = FALSE),
                   sw.obs = mean(avg.sw.obs, na.rm = FALSE),
                   temp.for = mean(temp.for, na.rm = FALSE), # force mean is NA if missing data
                   RH.for = mean(RH.for, na.rm = FALSE),
                   ws.for = mean(ws.for, na.rm = FALSE),
                   sw.for = mean(avg.sw.for, na.rm = FALSE),
                   doy = formattable(first(yday),4)) %>%
  ungroup() %>%
  filter(is.na(temp.for) == FALSE & is.na(RH.for) == FALSE && is.na(ws.for) == FALSE)
```

```{r plot states, daily average}
ggplot(data = joined.data.daily,aes(x = sw.for, y = sw.obs)) +
  geom_point(alpha = 0.8, color = "darkolivegreen4", size = .8) +
  geom_smooth(method = "lm", se = FALSE, color = "black", formula = y~x) +
  stat_poly_eq(formula = y~x, 
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
               parse = TRUE) +
  xlab("NOAA Forecast") +
  ylab("Site Observations") +
  # ggtitle("Temperature [C], Daily Measurements Comparison") + 
  ggtitle("Shortwave Radiation [W/m2]") +
  theme(text = element_text(size=15))
start_day = 0
end_day = 365
ggplot(data = joined.data.daily %>% filter(yday <=end_day & yday >= start_day)) +
  geom_line(aes(x = yday, y = sw.obs, color = "observations")) +
  geom_line(aes(x = yday, y = sw.for, color = "downscaled", group = NOAA.member)) + 
  scale_color_brewer(palette = "Set1") +
  # ylab("Temperature [C]") +
  ylab("Shortwave Radiaiton [W/m2]")
  xlab("day of year") +
  theme(legend.position="bottom", text = element_text(size=15))
```
```{r states: spatially downscaling step 1: spatially debias, add error}
joined.data.daily[,"group.num"] = row(joined.data.daily)[,1]
debiased.results <- daily_debias_and_add_error(joined.data.daily, nmembers = 10)
debiased <- debiased.results[[1]] %>%
  dplyr::mutate(yday = as.integer(doy))
debiased.with.noise <- debiased.results[[2]] %>%
  ungroup() %>%
  mutate(yday = as.integer(doy)) %>%
  select(-doy)
```

```{r plots from that last step}
joined.debiased.and.obs <- inner_join(debiased, joined.data.daily, by = "doy")
ggplot(data = joined.debiased.and.obs, aes(x = sw.mod, y = sw.obs)) +
  geom_point(alpha = 0.8, color = "darkolivegreen4", size = .8) +
  geom_smooth(method = "lm", se = FALSE, color = "black", formula = y~x) +
  stat_poly_eq(formula = y~x, 
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
               parse = TRUE) +
  xlab("Spatially Debiased NOAA Forecast") +
  ylab("Site Observations") +
  # ggtitle("Temperature [C], Daily Measurements Comparison") + 
  ggtitle("Shortwave [W/m2], Daily Measurements Comparison") + 
  theme(text = element_text(size=15))

start_day = 0
end_day = 365
ggplot() +
  geom_line(data = joined.data.daily %>% filter(yday <=end_day & yday >= start_day), aes(x = yday, y = sw.obs, color = "observations")) +
  geom_point(data = debiased %>% filter(doy <=end_day & doy >= start_day), aes(x = doy, y = sw.mod, color = "spatially debiased", group = NOAA.member)) + 
  scale_color_brewer(palette = "Set1") +
  # ylab("Temperature [C]") +
  ylab("Shortwave [W/m2]") +
  xlab("day of year") +
  theme(legend.position="bottom", text = element_text(size=15))

ggplot() +
  geom_line(data = joined.data.daily %>% filter(yday <=end_day & yday >= start_day), aes(x = yday, y = temp.obs, color = "observations")) +
  geom_point(data = debiased.with.noise %>% filter(yday <=end_day & yday >= start_day), aes(x = yday, y = temp.mod, color = "downscaled + spatially debiased", group = interaction(NOAA.member,dscale.member))) + 
  scale_color_brewer(palette = "Set1") +
  ylab("Temperature [C]") +
  xlab("day of year") +
  theme(legend.position="bottom", text = element_text(size=15))
```

```{r spatial downscaling step 2: redistribute across day}
NOAA.prop <- joined.data.original %>%
  dplyr::group_by(NOAA.member, yday) %>%
  dplyr::mutate(temp.for.mean = mean(temp.for),
                RH.for.mean = mean(RH.for),
                ws.for.mean = mean(ws.for)) %>%
  ungroup() %>%
  mutate(temp.prop = temp.for/temp.for.mean, # proportion of daily mean that each 6-hourly measurement is
         RH.prop = RH.for/RH.for.mean,
         ws.prop = ws.for/ws.for.mean) %>%
  select(NOAA.member, timestamp, doy, yday,temp.for, RH.for, ws.for, temp.for.mean, RH.for.mean, ws.for.mean, temp.prop, RH.prop, ws.prop)

# redistributed = 166 days * 21 NOAA members * 4 meas/day * 10 noise members
# 
redistributed <- inner_join(debiased %>% select(-doy), NOAA.prop, by = c("yday","NOAA.member")) %>%
  dplyr::group_by(NOAA.member, doy) %>%
  dplyr::mutate(ds.temp = temp.mod * temp.prop,
                ds.RH = RH.mod * RH.prop,
                ds.ws = ws.mod * ws.prop,
                dscale.member = NA) %>%
  ungroup() %>%
  select(NOAA.member, doy, yday, dscale.member, ds.temp, ds.RH, ds.ws)
# get list of days that have NAs for forecasts
imcomplete.days <- redistributed %>% 
  filter(is.na(ds.temp) | is.na(ds.ws) | is.na(ds.RH)) %>% 
  select(doy) %>% 
  mutate(doy = as.integer(doy)) %>% 
  unique()

redistributed.noise <- inner_join(debiased.with.noise, NOAA.prop, by = c("yday","NOAA.member")) %>%
  dplyr::group_by(NOAA.member, doy) %>%
  dplyr::mutate(ds.temp = temp.mod.noise * temp.prop,
                ds.RH = RH.mod.noise * RH.prop,
                ds.ws = ws.mod.noise * ws.prop) %>%
  ungroup() %>%
  select(NOAA.member, doy, yday, dscale.member, ds.temp, ds.RH, ds.ws)
```

```{r plots from last step}
ggplot(data = inner_join(redistributed, obs.units.match, by = c("doy")), aes(x = ds.temp, y = AirTC_Avg)) +
  geom_point(alpha = 0.3) +
    stat_poly_eq(formula = y~x, 
                  aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
                  parse = TRUE) +
  xlab("debiased forecast") +
  ylab("observations") +
  ggtitle("Temperature comparison without noise") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position="bottom", text = element_text(size=15))

ggplot(data = inner_join(redistributed.noise, obs.units.match, by = c("doy")), aes(x = ds.temp, y = AirTC_Avg)) +
  geom_point(alpha = 0.3) +
    stat_poly_eq(formula = y~x, 
                  aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
                  parse = TRUE) +
  xlab("debiased forecast") +
  ylab("observations") +
  ggtitle("Temperature comparison with added noise") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position="bottom", text = element_text(size=15))

start_day = 200
end_day = 210
ggplot() +
    geom_line(data = obs.units.match %>% filter(doy <=end_day & doy >= start_day), aes(x = doy, y = AirTC_Avg, color = "observations"), size = 1.5) +
  geom_point(data = redistributed %>% filter(doy <=end_day & doy >= start_day), aes(x = doy, y = ds.temp, group = NOAA.member, color = "debiased forecast redistributed")) +
  scale_color_brewer(palette = "Set1") +
  ylab("Temperature [C]") +
  xlab("day of year") +
  theme(legend.position="bottom", text = element_text(size=15)) +
  ggtitle("Temperature comparison no noise")

ggplot() +
    geom_line(data = obs.units.match %>% filter(doy <=end_day & doy >= start_day), aes(x = doy, y = AirTC_Avg, color = "observations"), size = 1.5) +
  geom_point(data = redistributed.noise %>% filter(doy <=end_day & doy >= start_day), aes(x = doy, y = ds.temp, group = NOAA.member, color = "debiased forecast redistributed")) +
  scale_color_brewer(palette = "Set1") +
  ylab("Temperature [C]") +
  xlab("day of year") +
  theme(legend.position="bottom", text = element_text(size=15)) +
  ggtitle("Temperature comparison with added noise")

```

```{r states: temporally downscale }
splined.ds <- new_spline_NOAA_offset(redistributed) %>%
  mutate(doy = formattable(round(doy,4),4)) %>%
  mutate(interp.temp = ifelse(as.integer(doy) %in% imcomplete.days$doy,NA, interp.temp),
         interp.ws = ifelse(as.integer(doy) %in% imcomplete.days$doy,NA, interp.ws),
         interp.RH = ifelse(as.integer(doy) %in% imcomplete.days$doy,NA, interp.RH))

splined.ds.noise <- new_spline_NOAA_offset(redistributed.noise) %>%
  mutate(doy = formattable(round(doy,4),4)) %>%
  # for days where NOAA was NA, the interp is set to NA
  mutate(interp.temp = ifelse(as.integer(doy) %in% imcomplete.days$doy,NA, interp.temp),
         interp.ws = ifelse(as.integer(doy) %in% imcomplete.days$doy,NA, interp.ws),
         interp.RH = ifelse(as.integer(doy) %in% imcomplete.days$doy,NA, interp.RH))

joined.obs.and.spline <- inner_join(obs.units.match, splined.ds, by = "doy")
joined.obs.and.spline.noise <- inner_join(obs.units.match, splined.ds.noise, by = "doy")

  formula = joined.obs.and.spline$AirTC_Avg ~ joined.obs.and.spline$interp.temp
  summary(lm(formula = formula))$r.squared
  
  formula = joined.obs.and.spline.noise$AirTC_Avg ~ joined.obs.and.spline.noise$interp.temp
  summary(lm(formula = formula))$r.squared
# ggplot(data = joined.obs.and.spline, aes(x = interp.temp, y = AirTC_Avg, alpha = 0.5)) +
#   geom_point() +
#   stat_poly_eq(formula = y~x, 
#                   aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
#                   parse = TRUE) +
#   xlab("debiased forecast") +
#   ylab("observations") +
#   ggtitle("Temperature comparison") +
#   scale_color_brewer(palette = "Set1") +
#   theme(legend.position="bottom", text = element_text(size=15))
# 
# ggplot(data = joined.obs.and.spline.noise, aes(x = interp.temp, y = AirTC_Avg, alpha = 0.5)) +
#   geom_point() +
#   stat_poly_eq(formula = y~x, 
#                   aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
#                   parse = TRUE) +
#   xlab("debiased forecast") +
#   ylab("observations") +
#   ggtitle("Temperature comparison") +
#   scale_color_brewer(palette = "Set1") +
#   theme(legend.position="bottom", text = element_text(size=15))
  
start_day = 200
end_day = 210
ggplot(data = joined.obs.and.spline %>% filter(doy <=end_day & doy >= start_day)) +
  geom_line(aes(x = doy, y = interp.temp, group = interaction(NOAA.member), color = "debiased forecast"), alpha = 0.5) +
  geom_line(aes(x = doy, y = AirTC_Avg, color = "observations"), size = 1.5) +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position="bottom", text = element_text(size=15))

ggplot(data = joined.obs.and.spline.noise %>% filter(doy <=end_day & doy >= start_day)) +
  geom_line(aes(x = doy, y = interp.temp, group = interaction(NOAA.member,dscale.member), color = "debiased forecast"), alpha = 0.5) +
  geom_line(aes(x = doy, y = AirTC_Avg, color = "observations"), size = 1.5) +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position="bottom", text = element_text(size=15))
```

```{r apply offset (but not to ws)}
offset <- joined.obs.and.spline %>%
  dplyr::mutate(doy.group = floor(doy)) %>%
  dplyr::group_by(NOAA.member, dscale.member, doy.group) %>% 
  dplyr::mutate(temp.offset = ifelse(hour == 4,interp.temp - AirTC_Avg, NA),
                temp.interp.ds = ifelse(hour >= 4, interp.temp - max(temp.offset, na.rm = TRUE), AirTC_Avg),
                ws.offset = 0, # not doing offset for ws
                ws.interp.ds = ifelse(hour >= 4, interp.ws - max(ws.offset, na.rm = TRUE), WS_ms_Avg),
                RH.offset = ifelse(hour == 4, interp.RH - RH, NA),
                RH.interp.ds = ifelse(hour >= 4, interp.RH - max(RH.offset, na.rm = TRUE), RH)) %>%
  ungroup()
  
offset.noise <- joined.obs.and.spline.noise %>%
  dplyr::mutate(doy.group = floor(doy)) %>%
  dplyr::group_by(NOAA.member, dscale.member, doy.group) %>% 
  dplyr::mutate(temp.offset = ifelse(hour == 4,interp.temp - AirTC_Avg, NA),
                temp.interp.ds = ifelse(hour >= 4, interp.temp - max(temp.offset, na.rm = TRUE), AirTC_Avg),
                ws.offset = 0, # not doing offset for ws
                ws.interp.ds = ifelse(hour >= 4, interp.ws - max(ws.offset, na.rm = TRUE), WS_ms_Avg),
                RH.offset = ifelse(hour == 4, interp.RH - RH, NA),
                RH.interp.ds = ifelse(hour >= 4, interp.RH - max(RH.offset, na.rm = TRUE), RH)) %>%
  ungroup()

formula = offset$AirTC_Avg ~ offset$temp.interp.ds # artificially high bc 12-4am is matches with obs
summary(lm(formula = formula))$r.squared
formula = offset.noise$AirTC_Avg ~ offset.noise$temp.interp.ds
summary(lm(formula = formula))$r.squared

# ggplot(data = offset, aes(x = temp.interp.ds, y = AirTC_Avg), alpha = 0.5) +
#   geom_point() + 
#   stat_poly_eq(formula = y~x, 
#                   aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
#                   parse = TRUE) +
#   xlab("debiased forecast") +
#   ylab("observations") +
#   ggtitle("Temperature comparison without noise") +
#   scale_color_brewer(palette = "Set1") +
#   theme(legend.position="bottom", text = element_text(size=15))
# 
# ggplot(data = offset.noise, aes(x = temp.interp.ds, y = AirTC_Avg), alpha = 0.5) +
#   geom_point() + 
#   stat_poly_eq(formula = y~x, 
#                   aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
#                   parse = TRUE) +
#   xlab("debiased forecast") +
#   ylab("observations") +
#   ggtitle("Temperature comparison with added noise") +
#   scale_color_brewer(palette = "Set1") +
#   theme(legend.position="bottom", text = element_text(size=15))

ggplot(data = offset %>% filter(doy <=end_day & doy >= start_day)) +
  geom_line(aes(x = doy, y = AirTC_Avg, color = "observations"), size = 1.5) +
  geom_line(aes(x = doy, y = temp.interp.ds, group = NOAA.member, color = "downscaled forecasts + offset")) +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position="bottom", text = element_text(size=15))
ggplot(data = offset.noise %>% filter(doy <=end_day & doy >= start_day)) +
  geom_line(aes(x = doy, y = AirTC_Avg, color = "observations"), size = 1.5) +
  geom_line(aes(x = doy, y = temp.interp.ds, group = interaction(NOAA.member,dscale.member), color = "downscaled forecasts + offset")) +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position="bottom", text = element_text(size=15))
  
```

```{r compare shortwave obs and forecast}
time.1 = as_datetime("2018-04-23 06:01:00")
obs.sw.comparison <- obs.units.match %>% mutate(group.num.2 = as.integer((timestamp - time.1)/(60*60*6))) %>%
  dplyr::group_by(group.num.2) %>%
  dplyr::summarize(avg.sw = mean(SR01Up_Avg),
                   timestamp = last(timestamp))
join.sw.comparison <- inner_join(obs.sw.comparison, forecast.units.match, by = "timestamp")

ggplot(data = join.sw.comparison, aes(x = avg.sw.y, y = avg.sw.x)) +
  geom_point(color = "darkolivegreen4", alpha = 0.5) +
  ggtitle("Comparison of 6-hourly Average Incoming Solar Radiation") +
  ylab("Observations") +
  xlab("NOAA Forecast") +
  geom_smooth(method = "lm", se = FALSE, color = "black", formula = y~x) +
  stat_poly_eq(formula = y~x, 
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
               parse = TRUE)
# in the future could debias the daily aggregate before doing other steps
  
```

```{r shortwave: solar geometry seasonal dynamics}
## solar geometry
inv =  1/24
start_day = 0
num_days = 365
end_day = start_day + num_days
doy = seq(start_day,end_day, by = inv)
lat = 37.307
lon = 360-79.837
yearly_geom = cbind(seq(0,365, by = inv),solar_geom(doy = seq(0,365, by = inv), lon, lat)) %>%
  as.data.frame()
print(ggplot(data = yearly_geom) +
  geom_line(aes(x = V1, y = V2), size = 0.3, alpha = 1, color = "red")) +
  ggtitle("Yearly Pattern in Incoming Shortwave Radiation") +
  ylab("Incoming Shortwave Radiation [W/m2]") +
  xlab("Day of Year")
```

```{r shortwave: temporally downscaling}

## visualze 6-hourly averages
# forecast.expanded <- forecast.units.match %>% group_by(group.num, avg.sw, timestamp, hour, NOAA.member) %>%
#   expand(doy = c(doy - 6/24,doy - 5/24,doy - 4/24, doy - 3/24,doy - 2/24,doy - 1/24, doy)) %>%
#   ungroup() # add times for past 6 hours (corresponding to each NOAA entry)
# 
# ggplot(data = forecast.expanded %>% filter(doy>200 & doy <205), aes(x = doy, y = avg.sw, group = NOAA.member)) +
#   geom_line() +
#   ylab("Mean Incoming Shortwave Radiation [W/m2]") +
#   xlab("Day of Year") +
#   ggtitle("Example of NOAA Shortwave Forecasts")

# could add ensemble members here for downscaling noise in future

sw.hours <- debiased.with.noise %>%
  dplyr::group_by(NOAA.member, yday) %>%
  tidyr::expand(hour = 0:23)
  
sw.ds <- debiased.with.noise %>% 
  select(sw.mod.noise, dscale.member, NOAA.member, yday) %>%
  dplyr::group_by(NOAA.member, yday, dscale.member) %>%
  inner_join(sw.hours, by = c("NOAA.member","yday")) %>%
  ungroup() %>%
  dplyr::mutate(doy = yday + hour/24) %>%
  dplyr::mutate(rpot = solar_geom(.$doy+4/24, lon, lat)) %>% # hourly sw flux calculated using solar geometry
  dplyr::group_by(yday) %>%
  dplyr::mutate(avg.rpot = mean(rpot)) %>% # daily sw mean from solar geometry
  ungroup() %>%
  dplyr::mutate(rpot.adj = ifelse(avg.rpot > 0, sw.mod.noise * (rpot/avg.rpot),0)) %>%
  dplyr::mutate(doy = formattable(doy,4)) # rpot.adj is the 6-houlry total from NOAA forecast (avg.sw) split into hourly values based on the shape of the solar_geom curve

start_day = 208
end_day = 210
tmp.sw.ds <- sw.ds %>% filter(doy >= start_day & doy <= end_day)
tmp.obs <- obs.units.match %>% filter(doy >= start_day & doy <= end_day)
tmp.mod = data.frame(doy = seq(start_day,end_day, by = inv), solar = solar_geom(seq(start_day,end_day, by = inv)+4/24, lon, lat))

alpha = 0.7
ggplot() +
  # geom_line(data =tmp.mod, aes(doy, solar), col = "red", alpha = alpha) +
  geom_line(data = tmp.sw.ds, aes(doy, rpot.adj, col = "Downscaled NOAA forecasts", group = interaction(NOAA.member, dscale.member)), alpha = alpha) +
      geom_line(data = tmp.obs, aes(doy, SR01Up_Avg, col = "Observations"), alpha = alpha) +
  scale_color_brewer(palette = "Set1") +
  ylab("Incoming Solar Radiation [W/m2]") +
  xlab("Day of Year")
# a mess right now with trying to match obs and ds at correct time, would like to join them later to asses the accuracy of the downscaling process
obs.sw.ds.comparison <- obs.units.match %>% select(SR01Up_Avg, hour, timestamp, doy, yday) %>% dplyr::group_by(yday, hour) %>% dplyr::summarize(avg.sw.hrly = mean(SR01Up_Avg, na.rm = TRUE), doy = formattable(first(yday) + first(hour)/24,4)) # added 1 hour to doy because downscaled times are reported as the average over the past hour, not the average over the current hour and adding 1 converts from treating is as current hour to past hour
# below works, but takes a long time to run because there's so many data points
# ds.shortwave.comparison <- inner_join(sw.ds, obs.sw.ds.comparison, by = c("doy"))
#  ggplot(data = ds.shortwave.comparison, aes(x = rpot.adj, y = avg.sw.hrly), alpha = 0.5) +
#    geom_point()
summary(lm(ds.shortwave.comparison$avg.sw.hrly~ds.shortwave.comparison$rpot.adj))$r.squared
lm(ds.shortwave.comparison$avg.sw.hrly~ds.shortwave.comparison$rpot.adj)$coefficients[2]

```


## old plotting stuff

var.name =  c("temp","RH","ws")
var.name.obs = c("AirTC_Avg","RH","WS_ms_Avg")
vars.title.list = c("Temperature [C]","Relative Humidity [%]","Average Wind Speed [m/s]")
# pdf("comparing daily_hourly_offset.pdf")
alpha = 0.3
for (i in 1:3){
  # daily mean comparisons
  my.formula <- y ~ x
  join.df <- inner_join(joined.data.daily %>% select(doy, temp.obs, RH.obs, ws.obs), debiased %>% select(-group.num), by = "doy") %>% unique()
  p1 <- ggplot(data = join.df, aes(y = get(paste(var.name[i],".obs", sep = "")), x = get(paste(var.name[i],".mod", sep = "")))) +   
    geom_point(data = joined.data.daily, aes(y = get(paste(var.name[i],".obs", sep = "")), x = get(paste(var.name[i],".for", sep = "")), col = "daily obs"), alpha = alpha) + 
    geom_point(aes(col = "debiased"), alpha = alpha) +
    geom_abline(aes(y = get(paste(var.name[i],".mod", sep = "")), x = get(paste(var.name[i],".obs", sep = ""))), slope = 1, intercept = 0, col = "red") +
    geom_smooth(method = "lm", se = FALSE, color = "black", formula = my.formula) +
    # stat_poly_eq(formula = my.formula, 
    #              aes(y = get(paste(var.name[i],".obs", sep = "")), x = get(paste(var.name[i],".mod", sep = "")), label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
    #              parse = TRUE) +
    ylab("Site Observations") + 
    xlab("NOAA forecast (original or debiased)") +
    scale_colour_brewer(palette = "Set1") +
    ggtitle(paste("Debiasing Daily Mean,", vars.title.list[i])) + 
    theme(legend.position="bottom", text = element_text(size=15))
  print(p1)
  
  # residuals from daily comparison
  p2 <- ggplot() +
    geom_point(data = joined.data.daily, aes(x = get(paste(var.name[i],".obs", sep = "")), y = get(paste(var.name[i],".for", sep = "")) - get(paste(var.name[i],".obs", sep = "")), color = "daily obs"), alpha = alpha) +
    geom_point(data = join.df, aes(x = get(paste(var.name[i],".obs", sep = "")), y = get(paste(var.name[i],".mod", sep = ""))- get(paste(var.name[i],".obs", sep = "")), color = "debiased"), alpha = alpha) + 
    scale_colour_brewer(palette = "Set1") +
    ggtitle(paste("residuals vs obs:", vars.title.list[i])) + 
    theme(legend.position="bottom") + 
    xlab("daily mean obs") + 
    ylab("redisuals (forecast - obs)")
  
  # get R2 for various steps
  print("6 hourly")
  formula = joined.data.original$temp.obs ~ joined.data.original$temp.for
  summary(lm(formula = formula))$r.squared
  print("daily aggregate")
  formula = joined.data.daily$temp.obs ~ joined.data.daily$temp.for
  summary(lm(formula = formula))$r.squared
  print("daily aggregate debiased + noise + spline + offset")
  formula = debiased.with.noise$temp.mod.noise ~ debiased.with.noise$
  print("daily aggregate debiased + spline")
  print("daily aggregate debiased + spline + offset")
  
  
  # # # offset method
  # p3 <- ggplot(data = offset, aes(y = get(var.name.obs[i]), x = get(paste("interp.",var.name[i], sep = "")))) +
  #   geom_point(aes(color = "hourly spline"), alpha = alpha) +
  #   geom_point(data = offset, aes(y = get(var.name.obs[i]), x = get(paste(var.name[i],".interp.ds", sep = "")), color = "hourly offset + spline + spatial downscaling"), alpha = alpha) +
  #   geom_smooth(method = "lm", se = FALSE, color = "black", formula = my.formula) +
  #   stat_poly_eq(formula = my.formula,
  #                aes(y = get(var.name.obs[i]), x = get(paste(var.name[i],".interp.ds", sep = "")), label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
  #                parse = TRUE) +
  #   ylab("original obs") +
  #   xlab("splined or spline + offset") +
  #   scale_colour_brewer(palette = "Set1") +
  #   ggtitle(paste("spline and offset:", vars.title.list[i])) +
  #   theme(legend.position="bottom")
  # 
  # p4 <- ggplot() +
  #   geom_point(data = offset, aes(y = get(var.name.obs[i]) - get(paste("interp.",var.name[i], sep = "")), x = get(paste("interp.",var.name[i], sep = "")), color = "residuals: hourly spline"), alpha = alpha) +
  #   geom_point(data = offset, aes(y = get(var.name.obs[i]) - get(paste(var.name[i],".interp.ds", sep = "")), x = get(paste(var.name[i],".interp.ds", sep = "")), color = "residuals: offset "), alpha = alpha) +
  #   scale_colour_brewer(palette = "Set1") +
  #   ggtitle(paste("residuals vs obs:", vars.title.list[i])) +
  #   theme(legend.position="bottom") +
  #   xlab("daily mean obs") +
  #   ylab("redisuals (forecast - obs)")
  start_day = 240
  end_day = 250
  p3 <- ggplot(data = offset %>% filter(doy <=end_day & doy >= start_day)) +
    geom_line(aes(x = doy, y = temp.interp.ds, color = "downscaled", group = interaction("NOAA.member", "dscale.member"))) + 
    geom_line(aes(x = doy, y = AirTC_Avg, color = "observations"))
  
  png(paste("./daily.downscale.spline.offset.1.2.3.4.",var.name[i], ".png", sep = ""), width = 1024, height = 768)
  grid.arrange(p1, p2, p3, p4, ncol = 2, nrow = 2)
  dev.off()
   readPNG(source = paste(paste("./p1.2.3.4.",var.name[i], ".png", sep = "")))
}
# dev.off()


  start_day = 200
  end_day = 210
  ggplot() +
    geom_line(data = offset %>% filter(doy <=end_day & doy >= start_day), aes(x = doy, y = get(paste("interp.",var.name[i], sep = "")), color = "ds + splined NOAA", group = interaction(NOAA.member,dscale.member)), alpha = alpha) + 
    geom_line(data = offset %>% filter(doy <= end_day & doy >= start_day), aes(x = doy, get(paste(var.name[i],".interp", ".ds",sep = "")), color = "ds + splined + offset", group = interaction(NOAA.member, dscale.member)), alpha = alpha) + 
    scale_colour_brewer(palette = "Set1") + 
    geom_line(data = offset %>% filter(doy <=end_day & doy >= start_day), aes(x = doy, y = get(var.name.obs[i]), color = "observations"), alpha = 1, size = 2) +
    ylab(paste(var.name[i]))

# scatter.original(joined.data, var.name[i], plot.title = paste("obs vs NOAA:", vars.title.list[i]))

# need to figure out what changed from last version to this one for r2 of temp daily aggregate to drop from 0.9 to 0.68

```

